---
title: "Practical G - Exercises"
author: "Statistical Programming in R"
date: ""
output: webexercises::webexercises_default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(webexercises)
```

---

#### Exercise 1


Create a new R Markdown document (default example) in HTML format. 

`r hide("Hint")`
Take a look in file menu
`r unhide()`

`r hide("Solution")`
File $\rightarrow$ New File $\rightarrow$ R Markdown   
`r unhide()`

Knit the document.

`r hide("Solution")`
Push the Knit button or Ctrl+Shift+K   
`r unhide()`

`r hide("Extra")`
It is also possible to use the command line with
```{r eval=FALSE}
rmarkdown::render(file, "html_document")
```
`r unhide()`


---

#### Exercise 2


Produce your own HTML report with R Markdown. Your work must contain text and at least one table and one figure. 


---

End of Practical

---

#### Useful References

- [Intro to Rmarkdown](https://rmarkdown.rstudio.com/articles_intro.html)
- [37: R For Data science](https://r4ds.had.co.nz/r-markdown.html)


---


